\documentclass[]{Keval-resume}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\documentclass[8pt]
\hypersetup{%
 	colorlinks=false,% hyperlinks will be black
 	linkbordercolor=red,% hyperlink borders will be red
 	pdfborderstyle={/S/U/W 0.2}% border style will be underline of width 0.25pt
}
\begin{document}
\namesection{\LARGE Preksha Shah}{
    % xxx-xxx-xxxx -> Phone Number
	\normalfont 978-654-1482 \textbullet{} Lowell , Massachusetts 01854 \textbullet{} \href{mailto:prekshashah025@gmail.com}{prekshashah025@gmail.com} \\
	 \href{https://https://www.linkedin.com/in/pshah07/}{\textbf{linkedin}.com/in/pshah07} \textbullet{}  \href{https://github.com/PrekshaShah-kelly}{\textbf{Github}\\
}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\hrulefill



\subsection{University of Massachusetts , Lowell\hfill \normalfont L\lowercase{owell}, M\lowercase{assachusetts}}
\position{Bachelors in Computer Science \normalfont   with specialization in Data Analytics}{May 2020}
\begin{flushleft}
\textbullet{} \textbf{Coursework:} Database Management , Data Mining , Statistics in Predictive Analytics , Data Qualitiy Analysis ,\linebreak  Data Visualization , Machine Learning , Optimization and Simulational Modelling  ,  Decision Analytics \\

\sectionsep

%\subsection{Government Engineering College Thrissur , Kerala \hfill \normalfont K\lowercase{erala}, I\lowercase{ndia}}
%\position{Bachelors  in Computer Science    \normalfont   ( specialization in \textbf{Data Analytics} )}{Aug 2015 - June 2019}


 %\textbullet{} \textbf{Coursework:} Data Mining , Machine Learning, Data structures and Algorithms, Data Analytics,  Computer Vision  \linebreak   , Network Security, Cryptography , Object Oriented Programming , Operating Systems. \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience} 
\hrulefill
\postsectionsep 

\subsection{ \href{https://www.ptc.com/}{PTC} \hfill \normalfont B\lowercase{oston,} M\lowercase{assachusetts} }
\position{Sr. Business Analyst}{Jun 2021 - Present}
\textbullet{} Data Manipulation and maintenance of Database for Metric and Project Level data using \textbf{Python libraries and DBT}.\linebreak
\textbullet{} Developing \textbf{Tableau} dashboards and visualizations for \textbf{recommending Metric improvements} to support cross functional teams. \\
\textbullet{} Analyze Product Telemetry Data to support Stakeholders decisions and Set team goals and Admin responsibilities. 

\sectionsep

\subsection{{Cigna HealthSprings} \hfill \normalfont A\lowercase{lpharetta,} G\lowercase{eorgia} }
\position{Business Analyst}{Jul 2020 - May 2021}
\textbullet{}Worked collaboratively with business and cross-functional teams to help them understand the user behaviors and take data driven decisions.
\linebreak
\textbullet{} Developed a strong working relationship with Cross functional Teams and Stakeholders and provided quality documentation support for business/functional requirements gathering, process analysis and product testing.

\sectionsep

\subsection{{Keshav Consulting} \hfill \normalfont A\lowercase{lpharetta,} G\lowercase{eorgia} }
\position{Business Analyst}{Jun 2019 - May 2020}
\textbullet{} Coordinated with business stakeholders to understand the business problems, proactively design best-suited, robust and \linebreak scalable data endpoint. \linebreak
\textbullet{} Built and analyzed dashboards and reports, establish key data sets to empower operational and exploratory analysis, evaluated \linebreak and defined metrics. \\

\sectionsep

\subsection{{Travobridge} \hfill \normalfont A\lowercase{hemdabad,} I\lowercase{ndia} }
\position{Data Analyst intern}{Jan 2019 - May 2019}
\textbullet{} Collaborated with developing team to develop product recommendation engine for customers increasing the sales by 25\%.\linebreak
\textbullet{} Extracted Data using\textbf{ SQL Server} queries from Snowflake \linebreak
\textbullet{}Coordinated with various stakeholders and teams to perform Stage-wise Analysis and provided Tableau Reports to back the \linebreak data.

\sectionsep

%\subsection{ARAMARK \hfill \normalfont L\lowercase{owell}, M\lowercase{assachusetts}}
%\position{Logistics Assistant}{Jan 2020 - Mar 2020}
%\textbullet{} Food services , logistics maintenance role and managing the frontdesk at University Dining.




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills} 
\hrulefill
\postsectionsep

\textbullet{} \textbf{Programming:} Python , SQL server , PostgreSQL , C++ \\
\textbullet{} \textbf{Applications:} Tableau , Power BI , Microsoft Excel , Microsoft Access ,  GIT  \\
\textbullet{} \textbf{Python Libraries:} Pandas , NumPy , XGboost , sklearn , SciPy , Matplotlib ,TensorFlow , Seaborn

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Project Highlights}
\hrulefill

% \textbullet{} Attention-based Joint Detection of Object and Semantic Part in \textbf{PyTorch} \href{https://arxiv.org/abs/2007.02419}{[\textbf{arXiv:2007.02419}]} \href{https://github.com/kevalmorabia97/Object-and-Semantic-Part-Detection-pyTorch}{[\textbf{Code}]}

% \textbullet{} Built an application in \textbf{JavaFX} for \textbf{Frequent Patterns \& Association Rule Mining} using Apriori algorithm \href{https://github.com/kevalmorabia97/FPARM-Frequent-Patterns-and-Association-Rule-Miner}{[\textbf{Code}]}

%%%%% ELABORATED FORMAT %%%%%

\position{Sentiment Analysis of Ukraine-Russia war }  {Present}
\textbullet{}  Predictive model for sentiment analysis of Text Reviews of social media comments using \textbf{ NLTK Library.} \\
\textbullet{}  Summarize and analyze the data of Russian equipment losses on each day of war in Ukraine \\


\sectionsep
\position{Sentiment analysisc of \textbf{COVID-19}}  {April 2021 - June 2021}
\textbullet{}  Extracting data from Twitter and Facebook using \textbf{Seobotsite social media bot} \\
\textbullet{} Data cleaning and topic modelling using \textbf{LDA} and used \textbf{LIWC} tool to generate scores for different emotions. \\
\textbullet{} Applied \textbf{Bert Model} for labelling the data and used \textbf{Woosh} for information retrieval process.


\sectionsep

\position{ \textbf{Dream Housing Finance Project}}  {November 2019 - January 2020}
\textbullet{}  Implemented various ML algorithms for classifying customers for loan using a combination of spatial and domain features. Accuracy of over \textbf{75 percent}. \\
\textbullet{} Developed a predictive model to improve and automate loan eligibility process. \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certification
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Certifications and Honors}
% \hrulefill
% \postsectionsep \linebreak
% \textbullet{}\textbf{Tableau Certified Analyst} \hfill{   August 2020} \linebreak
% \textbullet{}\textbf{Beta Gamma Sigma Honor Society member}  \hfill{ May 2021}\linebreak
% \textbullet{}\textbf{Data Mining Specialization} { - University of Illinois at Urbana-Champagne } \hfill{ April 2020}
% \linebreak
% \textbullet{}\textbf{Big Data Modeling and Management Systems} {-  UC San Diego} \hfill{June 2020}
% \linebreak

%

% \sectionsep

% commenting out the honors for now
\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP AND HONORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Leadership and Honors} 
\hrulefill




\begin{minipage}[t]{.78\textwidth}
	\textbullet{} Organized \textbf{TEDx Talks}  and \textbf{Hackathons}  as \textbf{Lead member} of the {Core Committee}
\end{minipage}%
\begin{minipage}[t]{.22\textwidth}
	\hfill April 2016 -May 2018
\end{minipage}
\begin{minipage}[t]{.78\textwidth}
	\textbullet{} Represented  state at \textbf{National Air Rifle Shooting Championship}{ in New Delhi , India}
\end{minipage}%
\begin{minipage}[t]{.22\textwidth}
	\hfill October 2016 
\end{minipage}

\begin{minipage}[t]{.78\textwidth}
	\textbullet{} Represented  state at \textbf{RBI National Level Quiz}{ in Kolkata , India}
\end{minipage}%
\begin{minipage}[t]{.22\textwidth}
	\hfill March 2015 
\end{minipage}
\begin{minipage}[t]{.78\textwidth}
	\textbullet{} Led the student council as the \textbf{School Head boy}
\end{minipage}%
\begin{minipage}[t]{.22\textwidth}
	\hfill September 2014 
\end{minipage}
\end{flushleft}
%\sectionsep
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\end{document}  \documentclass[]{article}
